%%% 
%%% Documentation/avm-examples.tex
%%% 
%%%     Copyright (C) 1999-2002 Andrew Lincoln Burrow
%%%     See license in text.
%%% 
%%%   - Examples for the ``alb-avm'' package.
%%% 
%%% $Id$
%%% 



\documentclass[11pt,a4paper,oneside]{article}



% 
% albCorp documentation style.
% 
% See: "~/Local/AlbCorpDoc/Documentation/alb-corp-doc-example.dvi".

\usepackage{alb-corp-doc}


% 
% The package being documented.

\usepackage{alb-avm}


% 
% Environment for full page width text.

\newenvironment{fullwidth}[0]{%
  \begin{list}{}{%
      \setlength{\topsep}{0pt}%
      \setlength{\leftmargin}{-\marginparwidth}%
      \addtolength{\leftmargin}{-\marginparsep}%
      \setlength{\listparindent}{\parindent}%
      \setlength{\itemindent}{0pt}%
      \setlength{\parsep}{\parskip}%
      }
  \item 
  }{%
  \end{list}
  }



\begin{document}



%%% 
%%% TITLE
%%% 

\albTitle{%
  Typesetting Attribute-Value Matrices Under \LaTeX{}%
}

\begin{albTitlePage}

  \albTitlePageSection{Author}

  Andrew Lincoln Burrow\\
  \texttt{alburrow@telus.net}\\
  \albLogo{} Corp%

  
  \albTitlePageSection{Abstract}
  
  The \texttt{alb-avm} package provides a single environment for type
  setting typed feature structures and inequated typed feature
  structures in attribute-value matrix (AVM) notation.  The package is
  supported by an emacs lisp file customising \AUCTeX{} to automate the
  insertion of typed feature structures.

  
  \albTitlePageSection{Copyright}

  Copyright \copyright{} 1999--2002 Andrew Lincoln Burrow.\\
  Permission is granted to copy, distribute and/or modify this
  document under the terms of the GNU Free Documentation License,
  Version 1.1 or any later version published by the Free Software
  Foundation; with no Invariant Sections, with no Front-Cover Texts,
  and with no Back-Cover Texts.  A copy of the license is included in
  Section~\ref{sec:alb-corp-doc:gnu-free-doc-license} entitled
  \emph{GNU Free Documentation License}.


  \albTitlePageSection{Version Information}

  \verb$Revision$\\
  \verb$Date$

\end{list}



%%% 
%%% INTRODUCTION
%%% 

\section{Introduction}
\label{sec:avm-examples:intr}

The \texttt{alb-avm} package provides a single environment for type
setting typed feature structures and inequated typed feature structures
in attribute-value matrix (AVM) notation.  The package is supported by
an emacs lisp file customising \AUCTeX{} to automate the insertion of
typed feature structures.

Section~\ref{sec:avm-examples:using-envir-comm} covers the use of the
\texttt{albAvm} environment and supporting commands.  The examples also
demonstrate a source code layout that is known to work well with
\AUCTeX{}.  Section~\ref{sec:avm-examples:auctex-cust} describes how the
commands are quickly entered under \AUCTeX{}.  This is the best way to
enter the AVM commands since it handles tags and source indentation
automatically.



%%% 
%%% USING THE ENVIRONMENTS AND COMMANDS
%%% 

\section{Using the Environments and Commands}
\label{sec:avm-examples:using-envir-comm}

Each topmost feature structure is represented by an instance of the
\texttt{albAvm} environment.  Within such an environment the
\texttt{albAvmType} command generates type labels, and the
\texttt{albAvmFeat} command generates feature-value pairs.  You must not
nest \texttt{albAvm} environments as nesting and tag numbering is
automated within the \texttt{albAvm} environment.  Instead, the
\texttt{albAvmFeat} and \texttt{albAvmTag} commands each take a second
arguments which is rendered as a nested substructure.


\subsection{Simple Feature Structures}
\label{sec:avm-examples:simple-feat-struct}

The most compact typed feature structure is a simple type.  It is the
only form expressed without nesting.  This simple form is just an
\texttt{albAvmType} command contained within an \texttt{albAvm}
environment, viz:
\begin{quote}
\begin{verbatim}
\begin{albAvm}
  \albAvmType{universal}
\end{albAvm}
\end{verbatim}
\end{quote}
which yields
\begin{quote}
  \begin{albAvm}
    \albAvmType{universal}
  \end{albAvm}
\end{quote}

Feature-values requires nesting.  This is achieved by placing the
contents of the feature-value as the second argument to the
\texttt{albAvmFeat} command.  Note that an \texttt{albAvm}-like
environment is automatically wrapped around the second argument to
\texttt{albAvmFeat}.  For example,
\begin{quote}
\begin{verbatim}
\begin{albAvm}
  \albAvmType{child}
  \albAvmFeat{FATHER}{%
    \albAvmType{human}
    }
  \albAvmFeat{MOTHER}{%
    \albAvmType{human}
    }
\end{albAvm}
\end{verbatim}
\end{quote}
yields
\begin{quote}  
  \begin{albAvm}
    \albAvmType{child}
    \albAvmFeat{FATHER}{%
      \albAvmType{human}
      }
    \albAvmFeat{MOTHER}{%
      \albAvmType{human}
      }
  \end{albAvm}
\end{quote}
Also, deeper nesting proceeds in the obvious way, so that 
\begin{quote}
\begin{verbatim}
\begin{albAvm}
  \albAvmType{child}
  \albAvmFeat{FATHER}{%
    \albAvmType{human}
    \albAvmFeat{MOTHER}{%
      \albAvmType{human}
      }
    \albAvmFeat{NAME}{%
      \albAvmType{name}
      }
    }
  \albAvmFeat{MOTHER}{%
    \albAvmType{human}
    }
\end{albAvm}
\end{verbatim}
\end{quote}
yields
\begin{quote}
  \begin{albAvm}
    \albAvmType{child}
    \albAvmFeat{FATHER}{%
      \albAvmType{human}
      \albAvmFeat{MOTHER}{%
        \albAvmType{human}
        }
      \albAvmFeat{NAME}{%
        \albAvmType{name}
        }
      }
    \albAvmFeat{MOTHER}{%
      \albAvmType{human}
      }
  \end{albAvm}
\end{quote}


\subsection{Feature Structures with Structure Sharing}
\label{sec:avm-examples:feat-struct-with-struct-s}

The \texttt{alb-avm} commands also provide for substructure tagging.
This is not automated by \LaTeX{} counters: automatic tags implemented
by extending the \LaTeX{} mechanism for labels and cross references is
beyond the scope of this implementation.  Instead tags must be
explicitly entered.  For a substructure to be tagged, place the tags as
the first argument to the \texttt{albAvmTag} command and place the
contents of the substructure as the second argument.  The
\texttt{albAvmTag} command occurs in place of the substructure.
Likewise, to refer to a substructure place the substructure's tag as the
only argument to the \texttt{albAvmRef} command.  This command also
occurs in place of the substructure.  For example, the liar sentence is
entered as
\begin{quote}
\begin{verbatim}
\begin{albAvm}
  \albAvmTag{1}{%
    \albAvmType{false}
    \albAvmFeat{ARG}{%
      \albAvmRef{1}
      }
    }
\end{albAvm}
\end{verbatim}
\end{quote}
which yields
\begin{quote}
  \begin{albAvm}
    \albAvmTag{1}{%
      \albAvmType{false}
      \albAvmFeat{ARG}{%
        \albAvmRef{1}
        }
      }
  \end{albAvm}
\end{quote}


\subsection{Inequated Feature Structures}
\label{sec:avm-examples:ineq-feat-struct}

Finally, provision is included for inequated feature structures.
Inequated feature structures are also entered using the \texttt{albAvm}
environment.  The initial part of the environment's body is entered like
a feature structure without inequations, excepting that all
substructures referred to in the inequations must be tagged.  The
remainder of the environment contains a comma separated list of
inequations.  Each inequation is entered with the \texttt{albAvmIneqtn}
command.  This command takes two arguments, which are simply the tags of
the substructures to be inequated.  For example,
\begin{quote}
\begin{verbatim}
\begin{albAvm}
  \albAvmType{house}
  \albAvmFeat{BEDROOM}{%
    \albAvmTag{1}{%
      \albAvmType{room}
      }
    }
  \albAvmFeat{KITCHEN}{%
    \albAvmTag{2}{%
      \albAvmType{room}
      }
    }
  \albAvmFeat{DININGROOM}{%
    \albAvmTag{3}{%
      \albAvmType{room}
      }
    }
  \albAvmFeat{LIVINGROOM}{%
    \albAvmTag{4}{%
      \albAvmType{room}
      }
    }
  \albAvmFeat{BATHROOM}{%
    \albAvmTag{5}{%
      \albAvmType{room}
      }
    }
  \albAvmIneqtn{1}{2}, \albAvmIneqtn{1}{5},
  \albAvmIneqtn{2}{5}, \albAvmIneqtn{3}{5},
  \albAvmIneqtn{4}{5}
\end{albAvmIneq}
\end{verbatim}
\end{quote}
yields
\begin{quote}
  \begin{albAvm}
    \albAvmType{house}
    \albAvmFeat{BEDROOM}{%
      \albAvmTag{1}{%
        \albAvmType{room}
        }
      }
    \albAvmFeat{KITCHEN}{%
      \albAvmTag{2}{%
        \albAvmType{room}
        }
      }
    \albAvmFeat{DININGROOM}{%
      \albAvmTag{3}{%
        \albAvmType{room}
        }
      }
    \albAvmFeat{LIVINGROOM}{%
      \albAvmTag{4}{%
        \albAvmType{room}
        }
      }
    \albAvmFeat{BATHROOM}{%
      \albAvmTag{5}{%
        \albAvmType{room}
        }
      }
    \albAvmIneqtn{1}{2}, \albAvmIneqtn{1}{5},
    \albAvmIneqtn{2}{5}, \albAvmIneqtn{3}{5},
    \albAvmIneqtn{4}{5} 
  \end{albAvm}
\end{quote}
 


%%% 
%%% AUCTEX CUSTOMISATIONS
%%% 

\section{\AUCTeX{} Customisations}
\label{sec:avm-examples:auctex-cust}

Under \AUCTeX{} the file \texttt{alb-avm.el} is automatically loaded
(subject to certain \AUCTeX{} configuration options).  This customises
\AUCTeX{} to automate the entry of AVM notation through a collection of
mutually recursive functions that interrogate the user for AVM input.

Automatic entry of AVM notation is triggered when an \texttt{albAvm}
environment is inserted by the \texttt{LaTeX-environment} command.  By
default \AUCTeX{} binds \texttt{LaTeX-environment} to the keys \texttt{C-c
  C-e}.  Automatic entry corresponds to a depth-first walk of the
feature structure.  At each substructure the user is prompted for
a description of the substructure.  The prompt contains the current
feature path to the substructure.

The first question about a substructure concerns its tag.  The history
list contains the tags entered for the feature structure.  If no value
is entered, then the tag is omitted; if the tag matches an existing tag,
then the substructure is represented by a simple reference to the
existing substructure; otherwise, the substructure is tagged with the
value.

Given a substructure has been allocated a new tag or no tag at all, it
must be explicitly constructed.  In this case the second question about
a substructure concerns its type.  The history list contains the types
entered during the current editing session.  If no value is entered,
then the substructure defaults to \texttt{universal} with the no
feature-values; otherwise, the type is recorded and feature-values
collected.  Feature-values are collected while non-empty strings are
returned for the features.  The history list contains the features
entered during the current editing session.  Recursion occurs in the
entry of the value part of the feature-values because each feature-value
is itself a substructure.

To prevent confusion while recursing into the substructures the prompt
strings are prefixed by the current path.  In addition, the source code
is incrementally entered with balanced parenthesis and indentation so
that it offers a useful cue to the substructure being defined.

As an exercise attempt to enter this feature structure:

\begin{quote}
  \begin{albAvm}
    \albAvmType{child}
    \albAvmFeat{FATHER}{%
      \albAvmType{human}
      \albAvmFeat{MOTHER}{%
        \albAvmType{human}
        }
      \albAvmFeat{NAME}{%
        \albAvmType{name}
        }
      }
    \albAvmFeat{MOTHER}{%
      \albAvmType{human}
      }
  \end{albAvm}
\end{quote}



%%% 
%%% LICENSE
%%% 

\section{GNU Free Documentation License}
\label{sec:alb-corp-doc:gnu-free-doc-license}

Version~1.1, March 2000\\[0.25\baselineskip]
Copyright \copyright\ 2000  Free Software Foundation,
Inc.\\[0.25\baselineskip]
59 Temple Place, Suite 330, Boston, MA  02111-1307  USA\\
Everyone is permitted to copy and distribute verbatim copies of this
license document, but changing it is not allowed.


\subsection*{Preamble}

The purpose of this License is to make a manual, textbook, or other
written document ``free'' in the sense of freedom: to assure everyone
the effective freedom to copy and redistribute it, with or without
modifying it, either commercially or noncommercially.  Secondarily, this
License preserves for the author and publisher a way to get credit for
their work, while not being considered responsible for modifications
made by others.

This License is a kind of ``copyleft'', which means that derivative
works of the document must themselves be free in the same sense.  It
complements the GNU General Public License, which is a copyleft license
designed for free software.

We have designed this License in order to use it for manuals for free
software, because free software needs free documentation: a free program
should come with manuals providing the same freedoms that the software
does.  But this License is not limited to software manuals; it can be
used for any textual work, regardless of subject matter or whether it is
published as a printed book.  We recommend this License principally for
works whose purpose is instruction or reference.


\subsection{Applicability and Definitions}
\label{sec:alb-corp-doc:appl-defin}

This License applies to any manual or other work that contains a notice
placed by the copyright holder saying it can be distributed under the
terms of this License.  The ``Document'', below, refers to any such
manual or work.  Any member of the public is a licensee, and is
addressed as ``you''.

A ``Modified Version'' of the Document means any work containing the
Document or a portion of it, either copied verbatim, or with
modifications and/or translated into another language.

A ``Secondary Section'' is a named appendix or a front-matter section of
the Document that deals exclusively with the relationship of the
publishers or authors of the Document to the Document's overall subject
(or to related matters) and contains nothing that could fall directly
within that overall subject.  (For example, if the Document is in part a
textbook of mathematics, a Secondary Section may not explain any
mathematics.)  The relationship could be a matter of historical
connection with the subject or with related matters, or of legal,
commercial, philosophical, ethical or political position regarding them.

The ``Invariant Sections'' are certain Secondary Sections whose titles
are designated, as being those of Invariant Sections, in the notice that
says that the Document is released under this License.

The ``Cover Texts'' are certain short passages of text that are listed,
as Front-Cover Texts or Back-Cover Texts, in the notice that says that
the Document is released under this License.

A ``Transparent'' copy of the Document means a machine-readable copy,
represented in a format whose specification is available to the general
public, whose contents can be viewed and edited directly and
straightforwardly with generic text editors or (for images composed of
pixels) generic paint programs or (for drawings) some widely available
drawing editor, and that is suitable for input to text formatters or for
automatic translation to a variety of formats suitable for input to text
formatters.  A copy made in an otherwise Transparent file format whose
markup has been designed to thwart or discourage subsequent modification
by readers is not Transparent.  A copy that is not ``Transparent'' is
called ``Opaque''.

Examples of suitable formats for Transparent copies include plain ASCII
without markup, Texinfo input format, \LaTeX{} input format, SGML or XML
using a publicly available DTD, and standard-conforming simple HTML
designed for human modification.  Opaque formats include PostScript,
PDF, proprietary formats that can be read and edited only by proprietary
word processors, SGML or XML for which the DTD and/or processing tools
are not generally available, and the machine-generated HTML produced by
some word processors for output purposes only.

The ``Title Page'' means, for a printed book, the title page itself,
plus such following pages as are needed to hold, legibly, the material
this License requires to appear in the title page.  For works in formats
which do not have any title page as such, ``Title Page'' means the text
near the most prominent appearance of the work's title, preceding the
beginning of the body of the text.


\subsection{Verbatim Copying}
\label{sec:alb-corp-doc:verb-copy}

You may copy and distribute the Document in any medium, either
commercially or noncommercially, provided that this License, the
copyright notices, and the license notice saying this License applies to
the Document are reproduced in all copies, and that you add no other
conditions whatsoever to those of this License.  You may not use
technical measures to obstruct or control the reading or further copying
of the copies you make or distribute.  However, you may accept
compensation in exchange for copies.  If you distribute a large enough
number of copies you must also follow the conditions in
Section~\ref{sec:alb-corp-doc:copy-quant}.

You may also lend copies, under the same conditions stated above, and
you may publicly display copies.


\subsection{Copying in Quantity}
\label{sec:alb-corp-doc:copy-quant}

If you publish printed copies of the Document numbering more than 100,
and the Document's license notice requires Cover Texts, you must enclose
the copies in covers that carry, clearly and legibly, all these Cover
Texts: Front-Cover Texts on the front cover, and Back-Cover Texts on the
back cover.  Both covers must also clearly and legibly identify you as
the publisher of these copies.  The front cover must present the full
title with all words of the title equally prominent and visible.  You
may add other material on the covers in addition.  Copying with changes
limited to the covers, as long as they preserve the title of the
Document and satisfy these conditions, can be treated as verbatim
copying in other respects.

If the required texts for either cover are too voluminous to fit
legibly, you should put the first ones listed (as many as fit
reasonably) on the actual cover, and continue the rest onto adjacent
pages.

If you publish or distribute Opaque copies of the Document numbering
more than 100, you must either include a machine-readable Transparent
copy along with each Opaque copy, or state in or with each Opaque copy a
publicly-accessible computer-network location containing a complete
Transparent copy of the Document, free of added material, which the
general network-using public has access to download anonymously at no
charge using public-standard network protocols.  If you use the latter
option, you must take reasonably prudent steps, when you begin
distribution of Opaque copies in quantity, to ensure that this
Transparent copy will remain thus accessible at the stated location
until at least one year after the last time you distribute an Opaque
copy (directly or through your agents or retailers) of that edition to
the public.

It is requested, but not required, that you contact the authors of the
Document well before redistributing any large number of copies, to give
them a chance to provide you with an updated version of the Document.


\subsection{Modifications}
\label{sec:alb-corp-doc:modif}

You may copy and distribute a Modified Version of the Document under the
conditions of Sections~\ref{sec:alb-corp-doc:verb-copy}
and~\ref{sec:alb-corp-doc:copy-quant} above, provided that you release
the Modified Version under precisely this License, with the Modified
Version filling the role of the Document, thus licensing distribution
and modification of the Modified Version to whoever possesses a copy of
it.  In addition, you must do these things in the Modified Version:

\begin{itemize}
\item Use in the Title Page (and on the covers, if any) a title distinct
  from that of the Document, and from those of previous versions (which
  should, if there were any, be listed in the History section of the
  Document).  You may use the same title as a previous version if the
  original publisher of that version gives permission.
\item List on the Title Page, as authors, one or more persons or
  entities responsible for authorship of the modifications in the
  Modified Version, together with at least five of the principal authors
  of the Document (all of its principal authors, if it has less than
  five).
\item State on the Title page the name of the publisher of the Modified
  Version, as the publisher.
\item Preserve all the copyright notices of the Document.
\item Add an appropriate copyright notice for your modifications
  adjacent to the other copyright notices.
\item Include, immediately after the copyright notices, a license notice
  giving the public permission to use the Modified Version under the
  terms of this License, in the form shown in the Addendum below.
\item Preserve in that license notice the full lists of Invariant
  Sections and required Cover Texts given in the Document's license
  notice.
\item Include an unaltered copy of this License.
\item Preserve the section entitled ``History'', and its title, and add
  to it an item stating at least the title, year, new authors, and
  publisher of the Modified Version as given on the Title Page.  If
  there is no section entitled ``History'' in the Document, create one
  stating the title, year, authors, and publisher of the Document as
  given on its Title Page, then add an item describing the Modified
  Version as stated in the previous sentence.
\item Preserve the network location, if any, given in the Document for
  public access to a Transparent copy of the Document, and likewise the
  network locations given in the Document for previous versions it was
  based on.  These may be placed in the ``History'' section.  You may
  omit a network location for a work that was published at least four
  years before the Document itself, or if the original publisher of the
  version it refers to gives permission.
\item In any section entitled ``Acknowledgements'' or ``Dedications'',
  preserve the section's title, and preserve in the section all the
  substance and tone of each of the contributor acknowledgements and/or
  dedications given therein.
\item Preserve all the Invariant Sections of the Document, unaltered in
  their text and in their titles.  Section numbers or the equivalent are
  not considered part of the section titles.
\item Delete any section entitled ``Endorsements''.  Such a section may
  not be included in the Modified Version.
\item Do not retitle any existing section as ``Endorsements'' or to
  conflict in title with any Invariant Section.
\end{itemize}

If the Modified Version includes new front-matter sections or appendices
that qualify as Secondary Sections and contain no material copied from
the Document, you may at your option designate some or all of these
sections as invariant.  To do this, add their titles to the list of
Invariant Sections in the Modified Version's license notice.  These
titles must be distinct from any other section titles.

You may add a section entitled ``Endorsements'', provided it contains
nothing but endorsements of your Modified Version by various parties --
for example, statements of peer review or that the text has been
approved by an organization as the authoritative definition of a
standard.

You may add a passage of up to five words as a Front-Cover Text, and a
passage of up to 25 words as a Back-Cover Text, to the end of the list
of Cover Texts in the Modified Version.  Only one passage of Front-Cover
Text and one of Back-Cover Text may be added by (or through arrangements
made by) any one entity.  If the Document already includes a cover text
for the same cover, previously added by you or by arrangement made by
the same entity you are acting on behalf of, you may not add another;
but you may replace the old one, on explicit permission from the
previous publisher that added the old one.

The author(s) and publisher(s) of the Document do not by this License
give permission to use their names for publicity for or to assert or
imply endorsement of any Modified Version.


\subsection{Combining Documents}
\label{sec:alb-corp-doc:comb-docum}

You may combine the Document with other documents released under this
License, under the terms defined in Section~\ref{sec:alb-corp-doc:modif}
above for modified versions, provided that you include in the
combination all of the Invariant Sections of all of the original
documents, unmodified, and list them all as Invariant Sections of your
combined work in its license notice.

The combined work need only contain one copy of this License, and
multiple identical Invariant Sections may be replaced with a single
copy.  If there are multiple Invariant Sections with the same name but
different contents, make the title of each such section unique by adding
at the end of it, in parentheses, the name of the original author or
publisher of that section if known, or else a unique number.  Make the
same adjustment to the section titles in the list of Invariant Sections
in the license notice of the combined work.

In the combination, you must combine any sections entitled ``History''
in the various original documents, forming one section entitled
``History''; likewise combine any sections entitled
``Acknowledgements'', and any sections entitled ``Dedications''.  You
must delete all sections entitled ``Endorsements.''


\subsection{Collections of Documents}
\label{sec:alb-corp-doc:coll-docum}

You may make a collection consisting of the Document and other documents
released under this License, and replace the individual copies of this
License in the various documents with a single copy that is included in
the collection, provided that you follow the rules of this License for
verbatim copying of each of the documents in all other respects.

You may extract a single document from such a collection, and distribute
it individually under this License, provided you insert a copy of this
License into the extracted document, and follow this License in all
other respects regarding verbatim copying of that document.


\subsection{Aggregation With Independent Works}
\label{sec:alb-corp-doc:aggr-with-indep-works}

A compilation of the Document or its derivatives with other separate and
independent documents or works, in or on a volume of a storage or
distribution medium, does not as a whole count as a Modified Version of
the Document, provided no compilation copyright is claimed for the
compilation.  Such a compilation is called an ``aggregate'', and this
License does not apply to the other self-contained works thus compiled
with the Document, on account of their being thus compiled, if they are
not themselves derivative works of the Document.

If the Cover Text requirement of
Section~\ref{sec:alb-corp-doc:copy-quant} is applicable to these copies
of the Document, then if the Document is less than one quarter of the
entire aggregate, the Document's Cover Texts may be placed on covers
that surround only the Document within the aggregate.  Otherwise they
must appear on covers around the whole aggregate.


\subsection{Translation}
\label{sec:alb-corp-doc:transl}

Translation is considered a kind of modification, so you may distribute
translations of the Document under the terms of
Section~\ref{sec:alb-corp-doc:modif}.  Replacing Invariant Sections with
translations requires special permission from their copyright holders,
but you may include translations of some or all Invariant Sections in
addition to the original versions of these Invariant Sections.  You may
include a translation of this License provided that you also include the
original English version of this License.  In case of a disagreement
between the translation and the original English version of this
License, the original English version will prevail.


\subsection{Termination}
\label{sec:alb-corp-doc:term}

You may not copy, modify, sublicense, or distribute the Document except
as expressly provided for under this License.  Any other attempt to
copy, modify, sublicense or distribute the Document is void, and will
automatically terminate your rights under this License.  However,
parties who have received copies, or rights, from you under this License
will not have their licenses terminated so long as such parties remain
in full compliance.


\subsection{Future Revisions of This License}
\label{sec:alb-corp-doc:future-revis-this-license}

The Free Software Foundation may publish new, revised versions of the
GNU Free Documentation License from time to time.  Such new versions
will be similar in spirit to the present version, but may differ in
detail to address new problems or concerns. See
http://www.gnu.org/copyleft/.

Each version of the License is given a distinguishing version number.
If the Document specifies that a particular numbered version of this
License ``or any later version'' applies to it, you have the option of
following the terms and conditions either of that specified version or
of any later version that has been published (not as a draft) by the
Free Software Foundation.  If the Document does not specify a version
number of this License, you may choose any version ever published (not
as a draft) by the Free Software Foundation.


\subsection*{ADDENDUM: How to use this License for your documents}

To use this License in a document you have written, include a copy of
the License in the document and put the following copyright and license
notices just after the title page:

\begin{quote}
  Copyright \copyright\ YEAR YOUR NAME.\\
  Permission is granted to copy, distribute and/or modify this document
  under the terms of the GNU Free Documentation License, Version 1.1 or
  any later version published by the Free Software Foundation; with the
  Invariant Sections being LIST THEIR TITLES, with the Front-Cover Texts
  being LIST, and with the Back-Cover Texts being LIST.  A copy of the
  license is included in the section entitled ``GNU Free Documentation
  License''.
\end{quote}

If you have no Invariant Sections, write ``with no Invariant Sections''
instead of saying which ones are invariant.  If you have no Front-Cover
Texts, write ``no Front-Cover Texts'' instead of ``Front-Cover Texts
being LIST''; likewise for Back-Cover Texts.

If your document contains nontrivial examples of program code, we
recommend releasing these examples in parallel under your choice of free
software license, such as the GNU General Public License, to permit
their use in free software.



\end{document}




%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
